A survey of HTTP caching options on the open Web

### 2015-01-14 sanity/paper1.tex
Future work
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@983 43ef1190-90fd-4dd7-a769-d0121f02b80e

Identify implementations that expose suitable caching headers.

@@

Monitor the change frequency and use a contingency table to assess the
correctness of caching headers.

Further investigate the correctness of the \rdfterm{dct:modified} property.

>>>>

In this work, we have only explored the cases where the server is
cooperative, in the sense that message data or metadata provides at
least a hint of a resource's cacheability. We also noted that the
majority of the Semantic Web is unhelpful. Therefore, an interesting
direction is to learn the change frequency of resources to use in a
heuristic freshness lifetime estimation. However, such work should
operate within the loose constraints of RFC7234, Section~4.2.2, and
should find it niche when the other techniques described in this paper
are unavailable. Once this is done, the correctness of caching headers
should be assessed, possibly using contingency tables.

@@

We found that some implementations are likely better than others, but
further understanding of these differences are impeded by the fact
that most \httph{Server} headers contained very little
information. Future work could seek more sophisticated fingerprinting
and understanding of the nature of these differences.

Further investigate the suitability of the \rdfterm{dct:modified}
property for estimating heuristic freshness.

For SPARQL Endpoints, it is interesting to examine the queries in a
shared proxy, e.g. an institutional cache or a Content
Delivery Network for frequent subpatterns, and prefetch and cache such
intermediate results so that subsequent queries can be answered in
part by the proxy.
